\bf Supplementary Material: Comparing the Power of Plot Designs to Reveal Correlation

### 2016-01-13 paper/paper.Rnw
SAS refit

<<setup, echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
library(ggplot2)
library(mnormt)
library(tidyr)
library(knitr)
library(nullabor)
library(dplyr)
library(mFilter)
library(grid)
library(gridExtra)
library(stringr)
#library(readr)
#library(lubridate)
# Convert these to read_csv at some point
correl <- read.csv("correlations.csv", stringsAsFactors = FALSE) ##Correlations of every plot in every lineup
full <- read.csv("full.csv", row.names=1, stringsAsFactors = FALSE) ##MTurk evaluations
prediction <- read.csv("sas/predfit.csv") ##Large file, very slow, fitted data from SAS
time.fit <- read.csv("sas/time.csv") ##coefficients for time model from SAS
powercoef <- read.csv("sas/PowerEstimates.csv") ##coefficients for power model from SAS

@@

#sasdata <- select(full.sub, rabs, n, alpha, rsgn, smoothed, design, subj_id, weights, correct, log_time)
#sasadata <- mutate(sasdata, rabs = as.numeric(rabs),
#                   subj_id = as.numeric(subj_id)
#                   design = ifelse(design=="Scatterplot", 1, 0))
#write.csv(subsetted, "sas/sasdata.csv", row.names = FALSE)
##The code that is exported to fit the model into SAS, see sas/model fit.sas

# data.frame(expand.grid(rabs=rabs, t=t, alpha=log(.05/0.95), rsgn=c(0,1),
#                                      smoothed=c(0,1), design=c(0,1),
#                                      subj_id=full.sub$subj_id))
#pred <- subset(pred, smoothed==0 | smoothed == 1 & t ==48 | smoothed ==1 & t ==96)
#write.csv(pred, "sas/predgrid.csv", row.names=FALSE) # these lines are done, but its a large file so commented out for knitr
#Code exported to SAS to predict new values

@@

\begin{figure}[htbp]
 \centering
<<powermodel, dependson='setup', fig.height=8, fig.width=8, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
predplot <- select(prediction, r, t, rsgn, smoothed, design, subj_id, RandomEf, FixedEf)
predplot <- mutate(prediction, RandomEf = exp(RandomEf)/(1+exp(RandomEf)), 
                   FixedEf = exp(FixedEf)/(1+exp(FixedEf)))
##Logit link function transform

@@

\begin{eqnarray} 
\label{timemodel}
ln(time_{ijklmt}) &=& \beta_{0} + \beta_{1} x_{1,i}  + \beta_{2} x_{2,j}  + \beta_{3} x_{3,k} + \beta_{4} x_{4,t} + \\
 & & \beta_{5} x_{1,i} \* x_{2,j} + \beta_{6} x_{5,l}\*(\beta_{7} + \beta_{8} x_{1,i}  + \beta_{9} x_{2,j}  + \beta_{10} x_{3,k} + \nonumber\\
 & & \beta_{11} x_{4,t} + \beta_{12} x_{1,i} \* x_{2,j}) + \beta_{13} x_{6,m} + \beta_{14} x_{5_l} \* x_{6,m} \gamma z_{s} + \epsilon_{ijklmt} \nonumber 
\end{eqnarray}

The structure of the model ~\ref{timemodel} is similar to that in Equation~\ref{modelpower} except the link function is replace with the identity function, $\psi(x) = x$, and a new variable, $x_{6,m}$, is introduced with $m = \{0,1\}$ indicating if the subject detected the true plot, where $m = 0$ is a failure to detect the true plot.

>>>>

<<setup, echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
library(ggplot2)
library(mnormt)
library(tidyr)
library(knitr)
library(nullabor)
library(dplyr)
library(mFilter)
library(grid)
library(gridExtra)
library(stringr)
#library(readr)
#library(lubridate)
# Convert these to read_csv at some point
correl <- read.csv("correlations.csv", stringsAsFactors = FALSE) ##Correlations of every plot in every lineup
full <- read.csv("full.csv", row.names=1, stringsAsFactors = FALSE) ##MTurk evaluations
prediction <- read.csv("sas/predfit.csv") ##fitted data from SAS
time.fit <- read.csv("sas/time.csv") ##coefficients for time model from SAS
powercoef <- read.csv("sas/PowerEstimates.csv") ##coefficients for power model from SAS

@@

#sasdata <- select(full.sub, rabs, n, alpha, rsgn, smoothed, design, subj_id, weights, correct, log_time)
#sasdata <- mutate(sasdata, rabs = as.numeric(rabs),
#                   subj_id = as.numeric(subj_id),
#                   design = ifelse(design=="Scatterplot", 1, 0))
#write.csv(sasdata, "sas/sasdata.csv", row.names = FALSE)
#The code that is exported to fit the model into SAS, see sas/model fit.sas

#pred <- data.frame(expand.grid(rabs=seq(0, 0.9, 0.01), t=c(12, 24, 48, 96), alpha=log(.05/0.95), rsgn=c(0,1),
#                                    smoothed=c(0,1), design=c(0,1),
#                                      subj_id = as.numeric(as.character(unique(full.sub$subj_id)))))
#pred <- subset(pred, smoothed==0 | smoothed == 1 & t ==48 | smoothed ==1 & t ==96)
#write.csv(pred, "sas/predgrid.csv", row.names=FALSE)
#Code exported to SAS to predict new values

@@

\begin{figure}[htbp]
 \centering
<<powermodel, dependson='setup', fig.height=8, fig.width=8, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
predplot <- prediction %>% filter(is.na(detected)) %>%
            select(r, t, rsgn, smoothed, design, subj_id, RandomEf, FixedEf) %>%
            mutate(RandomEf = exp(RandomEf)/(1+exp(RandomEf)), 
                   FixedEf = exp(FixedEf)/(1+exp(FixedEf)))
##Logit link function transform

@@

\begin{eqnarray} 
\label{timemodel}
ln(time_{ijklmt}) &=& \beta_{0} + \beta_{1} x_{1,i}  + \beta_{2} x_{2,j}  + \beta_{3} x_{3,k} + \beta_{4} x_{4,t} + \\
 & & \beta_{5} x_{1,i} \* x_{2,j} + \beta_{6} x_{5,l}\*(\beta_{7} + \beta_{8} x_{1,i}  + \beta_{9} x_{2,j}  + \beta_{10} x_{3,k} + \nonumber\\
 & & \beta_{11} x_{4,t} + \beta_{12} x_{1,i} \* x_{2,j}) + \gamma z_{s} + \epsilon_{ijklt} \nonumber 
\end{eqnarray}

The structure of the model ~\ref{timemodel} is similar to that in Equation~\ref{modelpower} except the link function is replace with the identity function, $\psi(x) = x$.

### 2016-01-13 paper/supplementary.Rnw
SAS refit

Analysing the level one residuals, $\hat{\epsilon_{i}}$ and level two residuals, $\hat{\gamma_{i}}$ allows us to test the model fit as described \citet{Loy}. There are some negative extreme outliers but the distributional assumption appears to hold.

>>>>

Analysing the level one residuals, $\hat{\epsilon_{i}}$, and level two residuals, $\hat{\gamma_{i}}$, allows us to test the model fit as described \citet{Loy}. There are some negative extreme outliers but the distributional assumption appears to hold.
